My title

### 2023-03-30 outputs/paper/paper.qmd
adding writeup for valence testing

This is pretty vague. I compared the valence scores of classical music tracks to see if this score is based on lyrics, or the audio itself.

@@

>>>>

This is pretty vague. I compared the valence scores of classical music tracks to see if this score is based on lyrics, or the audio itself. Jupiter's valence score is 326.78% higher than Mars. This not only indicates the valence is based on audio features other than lyrical content, but that it is capturing a difference between the two songs' profiles.

@@

#| echo: false
#| warning: false

sub_planets<- read.csv(here::here("inputs/data/subset_planets.csv"))
sub_planets |>
  select(artist_name, valence, track_name) |>
  head() |>
  knitr::kable(
    col.names = c("Artist Name", 
                  "Valence", 
                  "Track Name")
 )

I looked at the valence measures on Flight of the Bumblebee, a song that's much faster and "upbeat" than Mars and Jupiter. What I found complicated my understanding of valence -- different performance of the same song had different valence scores.

```{r}
# sub_planets<- read.csv(here::here("inputs/data/subset_planets.csv"))
# sub_planets |>
#   select(artist_name, valence, track_name) |>
#   head() |>
#   knitr::kable(
#     col.names = c("Artist Name", 
#                   "Valence", 
#                   "Track Name")
#  )
